Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-04 paper.tex
added references for NMRShiftDB and tried to clarify license

NMRShiftDB represents one of the earliest resources for Open
community-contributed data (first released in 2003). Research groups that 
measure NMR spectra or extract it from the literature can contribute that
information to
NMRShiftDB which provides an Open resource where
entries can be searched by chemical structure or properties
(especially peaks). Although it is difficult to
encourage large amounts of altruistic contribution (as happens with
Wikipedia), an alternative possible source of data could come from
linking
data capture with data publication. For example, the Blue Obelisk has
enough software that it is possible to create
a seamless chain for converting NMR structures in-house into
NMRShiftDB entries. If and when the chemistry community
encourages or requires semantic publication of spectra rather than
PDFs, it would be possible to populate NMRShiftDB rapidly
along the the lines of CrystalEye (see below).

@@

  \textbf{NMRShiftDB} & ? & Database of NMR spectra of organic compounds. \\ \hline

>>>>

NMRShiftDB \cite{nmrshiftdb, Steinbeck:2004do, Steinbeck2004} represents one of the earliest resources for Open
community-contributed data (first released in 2003). Research groups that 
measure NMR spectra or extract it from the literature can contribute that
information to
NMRShiftDB which provides an Open resource where
entries can be searched by chemical structure or properties
(especially peaks). Although it is difficult to
encourage large amounts of altruistic contribution (as happens with
Wikipedia), an alternative possible source of data could come from
linking
data capture with data publication. For example, the Blue Obelisk has
enough software that it is possible to create
a seamless chain for converting NMR structures in-house into
NMRShiftDB entries. If and when the chemistry community
encourages or requires semantic publication of spectra rather than
PDFs, it would be possible to populate NMRShiftDB rapidly
along the the lines of CrystalEye (see below).

@@

  \textbf{NMRShiftDB} & Public Domain & Database of NMR spectra of organic compounds. \\ \hline
